---
output: html_document
---

```{r set-options, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}

library(dplyr) # data munging and the pipe
library(tidyr) # wide to long dataframe
library(ggplot2) # plotting
library (knitr)

opts_chunk$set(echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE, 
                      error=FALSE)
read_chunk("plots.R")

```

```{r pre}
```

## Three Plots

### My Take on the Results of the Australian Marriage Law Postal Survey in 3 Static Plots

There have been a lot of great, useful interactive data summaries and visualizations published on the Australian Marriage Law Postal Survey results (e.g. [Australia Bureau of Statistics results summary](https://marriagesurvey.abs.gov.au/results/), [The Guardian's interactive full results by electorate](https://www.theguardian.com/australia-news/datablog/ng-interactive/2017/nov/15/same-sex-marriage-survey-how-australia-voted-electorate-by-electorate), [the ABC News results](http://www.abc.net.au/news/2017-11-15/same-sex-marriage-results-ssm/9145636)).

I love seeing the chloropleth maps of Australia with the overall State results, and I love sifting through results interactively electorate-by- electorate---a great presentation approach for users seeking information on a few key places. 

I find it hard to really see what is behind the State results without being about compare electorates visually all in the same space (e.g. in one plot or one one page). So I wondered if I could explore the data and create a small set of static data visualizations to explore the electorate results more closely, with a focus on being able to compare and contrast quickly. Sort of a data vizualization challenge to myself :)


#### Plot 1: State Results
```{r states, fig.width = 7, fig.height = 4}
```


#### Plot 2: Electorate Results
```{r divisions, fig.width = 9, fig.height = 6}
```

Data sourced from the [Australia Bureau of Statistics](https://marriagesurvey.abs.gov.au/results/downloads.html), released under the [CC BY 2.5 AU Licence](https://creativecommons.org/licenses/by/2.5/au/).
